Using Incremental Many-to-One Queries to Build a Fast and Tight Heuristic for A* in Road Networks

### 2021-11-17 paper/ch_potentials.tex
update CATCHUp Citation

A considerable amount of research and engineering effort has been put into studying the combination of traffic predictions with CH.
Several papers~\cite{bdsv-tdch-09,bgns-tdcha-10,klsv-dtdch-10,bgsv-mtdtt-13} and an entire dissertation~\cite{b-tdrpc-14} have been published on the subject.
Different variants with trade-offs regarding exactness, query speed and space consumption were proposed~\cite{bgsv-mtdtt-13}.
Recently, a new approach has been published~\cite{swz-sfert-20} which simultaneously achieves competitive results in all three aspects but only at the cost of considerable implementation complexity.

@@

The classical shortest path problem assumes that edge weights are scalars.
However, in practice, travel times vary along an edge due to the traffic situation.
% The primary reason is traffic.
Recurring traffic can be predicted by observing the traffic in the past.
It is common \cite{bgsv-mtdtt-13,bdpw-dtdrp-16,swz-sfert-20} to represent these predictions as \emph{travel time functions}.
An edge weight is no longer a scalar value but a function that maps the entry time onto the traversal time.
% Performing this prediction is outside of the scope of this paper.
% It is common to refer to routing with predicted traffic as \emph{time-dependent routing}.
% Again, we first formalize the extended problem setting and then describe our solution with CH-Potentials.

@@

For the preprocessing, we set $w_\ell(e) = \min_\tau w_q(e,\tau)$, that is the minimum travel time.
% With this setup, we extended CH-Potentials to support time-dependent routing.
By keeping travel time functions out of the CH, we avoid a lot of algorithmic complications compared to~\cite{bgsv-mtdtt-13,bdpw-dtdrp-16,swz-sfert-20,dn-crdtd-12} which have to create shortcuts of travel time functions.

>>>>

A considerable amount of research and engineering effort has been put into studying the combination of traffic predictions with CH.
Several papers~\cite{bdsv-tdch-09,bgns-tdcha-10,klsv-dtdch-10,bgsv-mtdtt-13} and an entire dissertation~\cite{b-tdrpc-14} have been published on the subject.
Different variants with trade-offs regarding exactness, query speed and space consumption were proposed~\cite{bgsv-mtdtt-13}.
Recently, a new approach has been published~\cite{swz-sfert-21} which simultaneously achieves competitive results in all three aspects but only at the cost of considerable implementation complexity.

@@

The classical shortest path problem assumes that edge weights are scalars.
However, in practice, travel times vary along an edge due to the traffic situation.
% The primary reason is traffic.
Recurring traffic can be predicted by observing the traffic in the past.
It is common \cite{bgsv-mtdtt-13,bdpw-dtdrp-16,swz-sfert-21} to represent these predictions as \emph{travel time functions}.
An edge weight is no longer a scalar value but a function that maps the entry time onto the traversal time.
% Performing this prediction is outside of the scope of this paper.
% It is common to refer to routing with predicted traffic as \emph{time-dependent routing}.
% Again, we first formalize the extended problem setting and then describe our solution with CH-Potentials.

@@

For the preprocessing, we set $w_\ell(e) = \min_\tau w_q(e,\tau)$, that is the minimum travel time.
% With this setup, we extended CH-Potentials to support time-dependent routing.
By keeping travel time functions out of the CH, we avoid a lot of algorithmic complications compared to~\cite{bgsv-mtdtt-13,bdpw-dtdrp-16,swz-sfert-21,dn-crdtd-12} which have to create shortcuts of travel time functions.
